Classical Planning Algorithms ¡ on the Atari Video Games: Preliminary Results

### 2014-11-07 workshop-paper/paper.tex

\begin{abstract}
\begin{quote}
The Atari  2600 games supported in  the Arcade Learning Environment (Bellemare et. al. 2013) 
all feature a known initial (RAM) state and actions that have deterministic effects. Classical planners, however, 
cannot be used  for selecting actions  for  two reasons: first,  no  compact PDDL-model of  the games is given, 
and  more importantly,  the action effects and goals are  not known a priori. Moreover, in these games there is usually  
no set of goals to be achieved but rewards to be collected. These features do not preclude the use of   classical  algorithms like
breadth-first search or Dijkstra's algorithm,  but    these methods are not effective over  large state spaces. We thus turn to a
different class of classical planning algorithms  introduced recently  that perform a \emph{structured exploration} of the state space; namely,  
like breadth-first search and Dijkstra's  algorithm they are ``blind'' and hence  do not require prior knowledge of state transitions, 
costs (rewards) or goals, and yet, like  heuristic search algorithms, they have been shown to be   effective for solving   problems over huge 
state spaces. The simplest such algorithm, called Iterated Width or \IW, consists of  a sequence of calls  $\IW(1)$, $\IW(2)$, 
.., $\IW(k)$ where  $\IW(i)$ is  
a breadth-first search in which a state is  pruned when it is not the first state in the search  to make true some set of i atoms or less.
Preliminary empirical results suggest that the performance of \IW\ with the  $k$ parameter fixed to $1$, 
i.e., $\IW(1)$, is much better than random or breadth-first search, and approaches 
the performance of \UCT. A simple best-first variation  of \IW,  that combine exploration and exploitation,
is evaluated as well. 
\end{quote}
\end{abstract}

@@

While all  these games feature a known initial (RAM) state and actions that
have deterministic effects on the state, the problem of selecting the next action
to be done cannot be addressed with state-of-the-art classical planners \cite{geffner:2013book}.
This is because there is  no compact PDDL-like encoding of the domain, and more 
importantly,  the goal to be achieved in each game  is not given. Indeed, there are 
often no goals  but rewards $r(a,s)$ that  depend on the action $a$ and 
the state $s$ in  which  the action is performed, and these rewards are not known a priori 
either.\footnote{Actually, in the Atari games, the rewards $r(a,s)$ depend only
on the state $f(a,s)$ that results from doing action $a$ in the state $s$.}
Thus no model of the  goals  or the  rewards can be used to bias the search, and hence, 
standard heuristic search and classical planning methods can't be used.

The action selection problem in the Atari games can be seen as a \emph{reinforcement learning} problem 
\cite{sutton:book} over a deterministic MDP where the state transitions and rewards are not known, or alternatively,
as a  \emph{net-benefit planning problem} \cite{ref-net-benefit-planning,keyder} with unknown state transitions  and  rewards. Namely, 
we seek  an action sequence $a_0, a_1, \ldots, a_m$ from the given current  state $s_0$ that generates 
a state sequence $s_0, s_1, \ldots, s_{m+1}$ with  maximum  total reward $\sum_{i=0}^{m} r(a_i,s_i)$,  
where $m$ is a sufficiently large planning horizon, and the rewards $r(a_i,s_i)$ and the  state-transitions $s_{i+1}=f(a_i,s_i)$ 
are known only after  action $a_i$ is applied in the state $s_i$.

The presence of unknown transition and  rewards in  the Atari games does not preclude the use of blind-search
methods like breadth-first search, Dijkstra's algorithm \cite{dijkstra},  or learning methods  such as 
LRTA* \cite{korf:lrta}, \UCT\ \cite{uct}, and Q-learning  \cite{sutton:rl,bertsekas:neuro}. Indeed, 
the net-benefit planning problem with unknown state transitions and rewards over a given planning
horizon, can be mapped into a standard \emph{shortest-path problem} which can be solved optimally by Dijkstra's algorithm.
For this, we just need to  map the unknown rewards $r(a,s)$ into positive (unknown) action costs $c(a,s) = C - r(a,s)$
where  $C$ is a large constant that exceeds the maximum possible reward. The fact that the state 
transition and cost functions  $f(a,s)$ and $c(a,s)$ are not known a priori doesn't affect the applicability of 
Dijkstra's algorithm, which requires the value of these functions precisely when  the action $a$
is applied in the state $s$.

@@

\Omit{
The sequence of calls IW(1), IW(2), \ldots, IW(k) manages to combine the scope of ``blind'' search algorithms with the performance of 
heuristic-search algorithms by exploring states  in an  order dictated by the ``width''  parameter $k$; 
states that have width 1 are explored first in linear time, then states that have  width two are explored in quadratic time, and so on. 
In classical planning problems, if the goal has a small width (something common in the classical planning domains when the  goal is a single atom, as
we have seen above), IW will find goal states  in low polynomial time. Similarly, in the reward-based setting, if  there are states of high reward 
that have small width, IW will find such states in low polynomial time, even if the state space is exponential in the number of variables. 
In this paper, we aim to test whether these ideas work for the Atari games too  when  the RAM state of the emulator
is used  as the system state. 
}

@@

For classical planning, the termination condition is the achievement of the goal. In the on-line setting, 
as in the Atari games, the termination condition is given by a time window or a maximum number of generated nodes.
The  best path found by \IW is the path  that has a  maximum accumulated reward. 
The accummulated reward $R(s)$  of a state $s$ reached in an iteration of \IW is determined by the  unique parent state $s'$ 
and action $a$ leading to $s$ from $s'$ as $R(s) = R(s') + r(a,s')$. The best state is the state $s$ with maximum reward
$R(s)$ generated but not pruned by \IW, and the best path is the one that leads to the state $s$ from the current state.
The action selected to be done next is then the first action along such a path.

@@

\caption{\small 
\emph{Top:} Number of classical planning problems  and percentages solved by $\IW(1)$, $\IW(2)$, or neither. Instances obtained
by splitting benchmarks  with $N$ atomic goals into $N$ problems with atomic goals.
\emph{Bottom:} Number of instances solved by \IW\ in comparison with  Iterative Deepening (\ID),  
Breadth-First Search (\BRFS),   and Greedy Best First Search (\textit{GBFS}) guided by  additive heuristic.
Time and  memory outs  after 30 minutes and 2 GB resp. From \cite{nir:ecai2102}.
}
\label{table1}
\end{table}
%%%%
%%%

@@

\IW\ is a systematic and complete blind-search algorithm like breadth-first search (\BRFS) and iterative deepening (ID),
but   unlike these algorithms, it uses the factored representation of the states in terms of variables to structure the 
search in a different way. This structured exploration  has proved to be very 
effective over classical planning benchmark domains  when goals are  single atoms.\footnote{
Any conjunctive goal can be mapped into a single dummy atomic goal by adding an action that
achieves the dummy goal and that has the original conjunctive goal as a precondition. 
Yet, this changes the domain.}
Table~\ref{table1} from \cite{nir:ecai2012} shows 
the percentage of instances that are  solved by  the first iteration of \IW, i.e.  $\IW(1)$, by the second iteration 
$\IW(2)$, and by neither one.  These are instances that  have been obtained from the existing benchmarks
by splitting problems with $N$ atomic goals, into $N$ problems with one atomic goal each. As the table shows, 
$37\%$ of the 37921 instances are solved by $\IW(1)$ while $51.3\%$ are  solved by $\IW(2)$. Since $\IW(k)$
runs in time that is exponential in $k$, this mean that almost $90\%$ of the 37921 instances are  solved in time that
is either linear or quadratic in the number of problem variables, which in these encodings are all \emph{boolean}.  
Furthermore, when the performance of \IW\   is compared with  breadth-first search and iterative deepening, 
on the one hand,  and  with a  Greedy Best First Search guided by the additive heuristic $h_{add}$ 
\cite{bonet:hsp-aij} on the other (this algorithm is similar 
to one used by  the FF planner when hill climbing search fails \cite{hoffmann:ff}), 
it turns out that ``blind'' \IW\ solves as many problems as the informed search, 34627 vs. 34849, far ahead
of the other blind algorithms BrFS and ID  that solve 9010 and 8762 problems each. This is shown in the bottom
part of the Table~\ref{table1}. Moreover, \IW\ is  faster and results in shorter plans than the heuristic search  
\cite{nir:ecai2012}.

@@

\IW\ is a purely exploration algorithm that does not take into account  the accumulated 
reward for selecting the next states to consider. As a simple, variant that combines
exploration and exploitation, we evaluated a \emph{best-first search} algorithm
with two queues: one queue  ordered first by  novelty measure 
(recall that novelty one means that the state is the first one to make some atom true),
and a second queue ordered by accumulated reward. In one iteration, the best first
search picks up the best node from one queue, and in the second iteration it picks
up the best node from the other queue. This way for combining multiple heuristics
is used in the LAMA planner \cite{richter:lama}, and was introduced in the
planner Fast Downward \cite{helmert:fd,malte:alternating}. In addition, we break ties
in the first queue favoring states with largest accumulated reward, and 
in the second queue, favoring states with smallest novelty measure. Last, when
a node is expanded, it is removed from the queue, and its children are placed on 
both queues. The exception are the nodes with no accumulated reward  that are 
placed in the first queue only. We refer to this best-first algorithm 
as \BFS.

@@

 \caption{\small Random baseline, \BRFS, $\IW(1)$, \BFS, \UCT~performance over 5 runs,
   setting the Atari 2600 random seeds to $0, \ldots, 4$, and maximum episode duration of $18,000$
   frames. For every algorithm, minus the trivial random baseline algorithm, we report the average CPU time per call 
   to each action selection algorithm, along with the average score achieved. \UCT~performance
   reported in \cite{bellemare:jair2013} is shown in parenthesis. Numbers
   in bold show best performer in terms of average score. Average score reported in 
   \cite{deep-mind-atari} is reported for reference under the column \Deepmind.
   }
\label{performance}

@@

The notion of width underlying the iterated width algorithm was developed in the context
of classical planning in order to understand why most of the hundreds of existing benchmarks
appear to be relatively simple for current planners, even
though classical planning is PSPACE-complete \cite{bylander}. A  partial answer is that 
most of these domains have a low width, and hence, can be solved in low polynomial time (by \IW)
when goals contain a single atom.  Benchmark problems with multiple atomic goals tend to be 
easy too, as the goals can often be achieved one at a time \cite{nir:ecai2012}.

@@

The use of ``novelty measures'' for guiding an optimization search while ignoring the function that is being
optimized, appears to be  common to novelty-based search methods developed independently 
in the context of genetic algorithms \cite{lehman:novelty}. %%% bibtex for this below
In these methods individuals in the population are not ranked according to the  optimization function
but in terms of how ``novel'' thay are in relation to the rest of the population, thus encouraging diversity
and exploration rather than (greedy) exploitation. The actual definition of novelty
in such a case is domain-dependent; for example, in the evolution of a controller
for guiding a robot in a maze, an individual controller  will not be ranked by how
close it takes the robot to the goal (the greedy measure), but how far it takes
the robot in relation to the locations that are reached when following the other controllers
(a diversity measure). The novelty measure used by \IW, on the other hand, is domain-independent and it 
is determined by the structure of the states as captured by the problem variables.

The balance between exploration and exploitation has received considerable attention in
reinforcement learning \cite{sutton:book}, where both are required for converging to an
optimal behavior. In the Atari games, as in other deterministic problems, however, ``exploration'' 
is not needed for optimality purposes, but just for improving the effectiveness of the 
 lookahead search. Indeed, a best-first search algorithm guided by (discounted)
accumulated reward will deliver eventually  best moves, but it will not be as effective
over small time windows, where like breadth-first search it's likely not to find any rewards
at all. The \UCT\ algorithm provides a method for balancing exploration and exploitation,
which  is  effective over small time windows. The \BFS\ algorithm above with two queues
that alternate, one guided by the novelty measures  and the other by the accumulated reward,
provides a different scheme. The first converges to the optimal behavior asymptotically; the 
second in a bounded number of steps. Alternatively, novelty-guided probes, possibly with 
some noise added, could potentially pay off as  a  base policy for \UCT\ in replacement 
of random rollouts, as they apparently manage to exploit the structure of many problems.

@@

We have shown experimentally that width-based algorithms like $\IW(1)$ and \BFS\ 
that originate in work in classical planning, can be used in the Atari games
with a performance that approaches the state-of-the-art, sometimes using a fraction of the time. We are currently addressing three 
issues, which we haven't managed to get in time for this submission. First, we want to extend the 
evaluation to all the games featured in \cite{bellemare:jair}, and to add more runs per  game. 
Second, we want to evaluate the various algorithms for different fixed time windows for decisions.
In the table above, for example, \UCT\ is often taking an order-of-magnitude more time per decision 
than  \BFS. Third, we need to revise the way duplicate states are handled in \IW\ and \BFS\ to ensure
that the best paths among the states that have been expanded are returned. Finally, 
for the future, we also want to explore whether this type of algorithms
can give meaningful results as well  when used on the screen state, as opposed 
to the RAM state.

>>>>

\begin{abstract}
\begin{quote}
The Atari  2600 games supported in  the Arcade Learning Environment (Bellemare et. al. 2013) 
all feature a known initial (RAM) state and actions that have deterministic effects. Classical planners, however, 
cannot be used  for selecting actions  for  two reasons: first,  no  compact PDDL-model of  the games is given, 
and  more importantly,  the action effects and goals are  not known \emph{a priori}. Moreover, in these games there is usually  
no set of goals to be achieved but rewards to be collected. These features do not preclude the use of   classical  algorithms like
breadth-first search or Dijkstra's algorithm,  but    these methods are not effective over  large state spaces. We thus turn to a
different class of classical planning algorithms  introduced recently  that perform a \emph{structured exploration} of the state space; namely,  
like breadth-first search and Dijkstra's  algorithm they are ``blind'' and hence  do not require prior knowledge of state transitions, 
costs (rewards) or goals, and yet, like  heuristic search algorithms, they have been shown to be   effective for solving   problems over huge 
state spaces. The simplest such algorithm, called Iterated Width or \IW, consists of  a sequence of calls  $\IW(1)$, $\IW(2)$, 
.., $\IW(k)$ where  $\IW(i)$ is  
a breadth-first search in which a state is  pruned when it is not the first state in the search  to make true some set of i atoms or less.
Preliminary empirical results suggest that the performance of \IW\ with the  $k$ parameter fixed to $1$, 
i.e., $\IW(1)$, is much better than random or breadth-first search, and approaches 
the performance of \UCT. A simple best-first variation  of \IW,  that combine exploration and exploitation,
is evaluated as well. 
\end{quote}
\end{abstract}

@@

While all  these games feature a known initial (RAM) state and actions that
have deterministic effects on the state, the problem of selecting the next action
to be done cannot be addressed with state-of-the-art classical planners \cite{geffner:book}.
This is because there is  no compact PDDL-like encoding of the domain, and more 
importantly,  the goal to be achieved in each game  is not given. Indeed, there are 
often no goals  but rewards $r(a,s)$ that  depend on the action $a$ and 
the state $s$ in  which  the action is performed, and these rewards are not known a priori 
either.\footnote{Actually, in the Atari games, the rewards $r(a,s)$ depend only
on the state $f(a,s)$ that results from doing action $a$ in the state $s$.}
Thus no model of the  goals  or the  rewards can be used to bias the search, and hence, 
standard heuristic search and classical planning methods can't be used.

The action selection problem in the Atari games can be seen as a \emph{reinforcement learning} problem 
\cite{sutton:book} over a deterministic MDP where the state transitions and rewards are not known, or alternatively,
as a  \emph{net-benefit planning problem} \cite{coles2012survey,keyder:jair09} with unknown state transitions  and  rewards. Namely, 
we seek  an action sequence $a_0, a_1, \ldots, a_m$ from the given current  state $s_0$ that generates 
a state sequence $s_0, s_1, \ldots, s_{m+1}$ with  maximum  total reward $\sum_{i=0}^{m} r(a_i,s_i)$,  
where $m$ is a sufficiently large planning horizon, and the rewards $r(a_i,s_i)$ and the  state-transitions $s_{i+1}=f(a_i,s_i)$ 
are known only after  action $a_i$ is applied in the state $s_i$.

The presence of unknown transition and  rewards in  the Atari games does not preclude the use of blind-search
methods like breadth-first search, Dijkstra's algorithm \cite{dijkstra},  or learning methods  such as 
LRTA* \cite{korf:lrta}, \UCT\ \cite{uct}, and Q-learning  \cite{sutton:book,bertsekas:neuro}. Indeed, 
the net-benefit planning problem with unknown state transitions and rewards over a given planning
horizon, can be mapped into a standard \emph{shortest-path problem} which can be solved optimally by Dijkstra's algorithm.
For this, we just need to  map the unknown rewards $r(a,s)$ into positive (unknown) action costs $c(a,s) = C - r(a,s)$
where  $C$ is a large constant that exceeds the maximum possible reward. The fact that the state 
transition and cost functions  $f(a,s)$ and $c(a,s)$ are not known a priori doesn't affect the applicability of 
Dijkstra's algorithm, which requires the value of these functions precisely when  the action $a$
is applied in the state $s$.

@@

% \Omit{
% The sequence of calls IW(1), IW(2), \ldots, IW(k) manages to combine the scope of ``blind'' search algorithms with the performance of 
% heuristic-search algorithms by exploring states  in an  order dictated by the ``width''  parameter $k$; 
% states that have width 1 are explored first in linear time, then states that have  width two are explored in quadratic time, and so on. 
% In classical planning problems, if the goal has a small width (something common in the classical planning domains when the  goal is a single atom, as
% we have seen above), IW will find goal states  in low polynomial time. Similarly, in the reward-based setting, if  there are states of high reward 
% that have small width, IW will find such states in low polynomial time, even if the state space is exponential in the number of variables. 
% In this paper, we aim to test whether these ideas work for the Atari games too  when  the RAM state of the emulator
% is used  as the system state. 
% }

@@

For classical planning, the termination condition is the achievement of the goal. In the on-line setting, 
as in the Atari games, the termination condition is given by a time window or a maximum number of generated nodes.
The  best path found by \IW is the path  that has a  maximum accumulated reward. 
The accumulated reward $R(s)$  of a state $s$ reached in an iteration of \IW is determined by the  unique parent state $s'$ 
and action $a$ leading to $s$ from $s'$ as $R(s) = R(s') + r(a,s')$. The best state is the state $s$ with maximum reward
$R(s)$ generated but not pruned by \IW, and the best path is the one that leads to the state $s$ from the current state.
The action selected to be done next is then the first action along such a path.

@@

\caption{\small 
\emph{Top:} Number of classical planning problems  and percentages solved by $\IW(1)$, $\IW(2)$, or neither. Instances obtained
by splitting benchmarks  with $N$ atomic goals into $N$ problems with atomic goals.
\emph{Bottom:} Number of instances solved by \IW\ in comparison with  Iterative Deepening (\ID),  
Breadth-First Search (\BRFS),   and Greedy Best First Search (\textit{GBFS}) guided by  additive heuristic.
Time and  memory outs  after 30 minutes and 2 GB resp. From \cite{nir:ecai2012}.
}
\label{table1}
\end{table}
%%%%
%%%

@@

\IW\ is a systematic and complete blind-search algorithm like breadth-first search (\BRFS) and iterative deepening (ID),
but   unlike these algorithms, it uses the factored representation of the states in terms of variables to structure the 
search in a different way. This structured exploration  has proved to be very 
effective over classical planning benchmark domains  when goals are  single atoms.\footnote{
Any conjunctive goal can be mapped into a single dummy atomic goal by adding an action that
achieves the dummy goal and that has the original conjunctive goal as a precondition. 
Yet, this changes the domain.}
Table~\ref{table1} from \cite{nir:ecai2012} shows 
the percentage of instances that are  solved by  the first iteration of \IW, i.e.  $\IW(1)$, by the second iteration 
$\IW(2)$, and by neither one.  These are instances that  have been obtained from the existing benchmarks
by splitting problems with $N$ atomic goals, into $N$ problems with one atomic goal each. As the table shows, 
$37\%$ of the 37921 instances are solved by $\IW(1)$ while $51.3\%$ are  solved by $\IW(2)$. Since $\IW(k)$
runs in time that is exponential in $k$, this mean that almost $90\%$ of the 37,921 instances are  solved in time that
is either linear or quadratic in the number of problem variables, which in these encoding are all \emph{boolean}.  
Furthermore, when the performance of \IW\   is compared with  breadth-first search and iterative deepening, 
on the one hand,  and  with a  Greedy Best First Search guided by the additive heuristic $h_{add}$ 
\cite{bonet:aij-hsp} on the other (this algorithm is similar 
to one used by  the FF planner when hill climbing search fails \cite{hoffmann:ff}), 
it turns out that ``blind'' \IW\ solves as many problems as the informed search, 34,627 vs. 34,849, far ahead
of the other blind algorithms \BRFS\ and \ID\  that solve 9,010 and 8,762 problems each. This is shown in the bottom
part of the Table~\ref{table1}. Moreover, \IW\ is  faster and results in shorter plans than the heuristic search  
\cite{nir:ecai2012}.

@@

\IW\ is a purely exploration algorithm that does not take into account  the accumulated 
reward for selecting the next states to consider. As a simple, variant that combines
exploration and exploitation, we evaluated a \emph{best-first search} algorithm
with two queues: one queue  ordered first by  novelty measure 
(recall that novelty one means that the state is the first one to make some atom true),
and a second queue ordered by accumulated reward. In one iteration, the best first
search picks up the best node from one queue, and in the second iteration it picks
up the best node from the other queue. This way for combining multiple heuristics
is used in the LAMA planner \cite{richter:lama}, and was introduced in the
planner Fast Downward \cite{helmert:fd}. In addition, we break ties
in the first queue favoring states with largest accumulated reward, and 
in the second queue, favoring states with smallest novelty measure. Last, when
a node is expanded, it is removed from the queue, and its children are placed on 
both queues. The exception are the nodes with no accumulated reward  that are 
placed in the first queue only. We refer to this best-first algorithm 
as \BFS.

@@

 \caption{\small Random baseline, \BRFS, $\IW(1)$, \BFS, \UCT~performance over 5 runs,
   setting the Atari 2600 random seeds to $0, \ldots, 4$, and maximum episode duration of $18,000$
   frames. For every algorithm, minus the trivial random baseline algorithm, we report the average CPU time per call 
   to each action selection algorithm, along with the average score achieved. \UCT~performance
   reported in \cite{bellemare:jair2013} is shown in parenthesis. Numbers
   in bold show best performer in terms of average score.
   }
\label{performance}

@@

The notion of width underlying the iterated width algorithm was developed in the context
of classical planning in order to understand why most of the hundreds of existing benchmarks
appear to be relatively simple for current planners, even
though classical planning is PSPACE-complete \cite{bylander:complexity}. A  partial answer is that 
most of these domains have a low width, and hence, can be solved in low polynomial time (by \IW)
when goals contain a single atom.  Benchmark problems with multiple atomic goals tend to be 
easy too, as the goals can often be achieved one at a time \cite{nir:ecai2012}.

@@

The use of ``novelty measures'' for guiding an optimization search while ignoring the function that is being
optimized, appears to be  common to novelty-based search methods developed independently 
in the context of genetic algorithms \cite{lehman:novelty}. %%% bibtex for this below
In these methods individuals in the population are not ranked according to the  optimization function
but in terms of how ``novel'' they are in relation to the rest of the population, thus encouraging diversity
and exploration rather than (greedy) exploitation. The actual definition of novelty
in such a case is domain-dependent; for example, in the evolution of a controller
for guiding a robot in a maze, an individual controller  will not be ranked by how
close it takes the robot to the goal (the greedy measure), but how far it takes
the robot in relation to the locations that are reached when following the other controllers
(a diversity measure). The novelty measure used by \IW, on the other hand, is domain-independent and it 
is determined by the structure of the states as captured by the problem variables.

The balance between exploration and exploitation has received considerable attention in
reinforcement learning \cite{sutton:book}, where both are required for converging to an
optimal behavior. In the Atari games, as in other deterministic problems, however, ``exploration'' 
is not needed for optimality purposes, but just for improving the effectiveness of the 
 lookahead search. Indeed, a best-first search algorithm guided by (discounted)
accumulated reward will deliver eventually  best moves, but it will not be as effective
over small time windows, where like breadth-first search it's likely not to find any rewards
at all. The \UCT\ algorithm provides a method for balancing exploration and exploitation,
which  is  effective over small time windows. The \BFS\ algorithm above with two queues
that alternate, one guided by the novelty measures  and the other by the accumulated reward,
provides a different scheme. The first converges to the optimal behavior asymptotically; the 
second in a bounded number of steps. Alternatively, novelty-guided probes, possibly with 
some noise added, could potentially pay off as  a  base policy for \UCT\ in replacement 
of random roll outs, as they apparently manage to exploit the structure of many problems.

@@

We have shown experimentally that width-based algorithms like $\IW(1)$ and \BFS\ 
that originate in work in classical planning, can be used in the Atari games
with a performance that approaches the state-of-the-art, sometimes using a fraction of the time. We are currently addressing three 
issues, which we haven't managed to get in time for this submission. First, we want to extend the 
evaluation to all the games featured in \cite{bellemare:jair2013}, and to add more runs per  game. 
Second, we want to evaluate the various algorithms for different fixed time windows for decisions.
In the table above, for example, \UCT\ is often taking an order-of-magnitude more time per decision 
than  \BFS. Third, we need to revise the way duplicate states are handled in \IW\ and \BFS\ to ensure
that the best paths among the states that have been expanded are returned. Finally, 
for the future, we also want to explore whether this type of algorithms
can give meaningful results as well  when used on the screen state, as opposed 
to the RAM state.
